Handling String-Number Conversion in String Constraint Solving

### 2019-11-09 evaluation.tex

\todo{Organize/Revise the context; Revise tables; Discussions}

{\bf General description}:
In this section, we report and discuss our experiments. As a base result, we compare z3-Trau to SMT tools z3 and CVC4 on PyEx benchmark which is widely used for testing SMT string solvers to show the performance of z3-Trau in general. Then we do the same comparison on our string\_to\_int benchmarks to evaluate our approach.

{\bf How we obtained our (str\_int) benchmark}:
For experiments, we prepared our own str\_int benchmark\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}. It is collected from two sources of Python programs: Leetcode solutions written in Python and Python core libraries. These Python programs are concolic tested by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs. The SMT queries during the concolic testing are collected to the benchmark. The benchmark has two versions: full\_str\_int and filtered\_str\_int. full\_str\_int is the original benchmark we collected; filtered\_str\_int is that we filtered out cases that cvc4 says unsat while the unsat corers are not containing \texttt{str.to.int} or \texttt{int.to.str}.

{\bf The environment of experiments}:
The experiments are conducted under machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. Since the large amount of problems in these benchmarks, we use containers to run these experiments in several machines with the same environment. The timeout is set to 10 seconds.

{\bf Some annotations in tables}:
\texttt{u.k.} stands for ``unknown''. \texttt{t.o.} stands for ``timeout''. \texttt{error} means that the execution is stopped with an error or exception such as segmental fault. \texttt{misc} means that the execution ends without expected (including errors) output.

{\bf Tabales}:
Table~\ref{table:base_benchmark} shows the comparison on several string benchmarks that are used by other tools. The total amount of cases in PyEx is 25421.

\begin{table*}[]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19655 & 3851 & 1915/0 & 19763 & 3834 & 0/1824 & 16578 & 3832 & 5011/0 & 3023 & 3835 & 16717/1846 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 36 & 112 & 105/347 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 676 & 1780 &  70/140 \\ 
StringFuzz	& 504 & 295 & 264/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 184 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 2021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

Table~\ref{table:str_int_benchmark} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
\begin{table*}[]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
full\_str\_int		& 3289 & 17089 & 1195/0 & 2185 & 16377 & 3011/0 & 2716 & 16831 & 2026/0 & 422 & 16034 & 4131/986 \\ 
filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}

>>>>

\todo{Organize/Revise the context; Add references of benchmarks; Revise tables; Discussions}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19655 & 3851 & 1915/0 & 19763 & 3834 & 0/1824 & 16578 & 3832 & 5011/0 & 3023 & 3835 & 16717/1846 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 36 & 112 & 105/347 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 676 & 1780 &  70/140 \\ 
StringFuzz	& 504 & 295 & 264/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 2021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
full\_str\_int		& 3289 & 17089 & 1195/0 & 2185 & 16377 & 3011/0 & 2716 & 16831 & 2026/0 & 422 & 16034 & 4131/986 \\ 
filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}

In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation. To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[]; 
LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[]. Table~\ref{table:base_benchmark} shows the result of the comparison. The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. We set the timeout is to 10 seconds. Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster. The results are either sat, unsat, timeout, or $\times$. $\times$ may be unknown, error, or exception.

\textbf{Comparison according to Table 1......}

To evaluate our strategy for string-number/number-string conversion, we also prepared a benchmark \texttt{str\_int}\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}. It is collected from two sources of Python programs that use ttexttt{int()} function: Leetcode solutions written in Python and Python core libraries. We concolic tested these Python programs by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs. The SMT queries during the concolic testing are collected as our benchmark. To be more precise in evalutation, we have two versions of \texttt{str\_int} benchmark: \texttt{full\_str\_int} and \texttt{filtered\_str\_int}. \texttt{full\_str\_int} is the original benchmark we collected (i.e. from Python programs using \texttt{int()}); \texttt{filtered\_str\_int} is a subset of \texttt{fill\_str\_int}. We filtered out problems that cvc4 says unsat while the unsat cores do not contain \texttt{str.to.int} or \texttt{int.to.str}. The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}. The experiments are conducted under the same condition as the experiments on other benchmarks.

\textbf{Comparison according to Table 2.....}
